Modelling fine-scale correlation structures using hidden Markov models

### 2020-07-13 Report/main.tex
Commit before changing STFT to Fourier Transform
Update appendix - before moving tables and figures
Small Edits

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{psfrag}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}

\input{header}
\input{defs}

@@

% User-defined commands go here
\renewcommand{\eqref}[1]{(\ref{#1})}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mt}[1]{\mathrm{#1}}
\newcommand{\rv}{random variable}

% Title, authors, affiliations
\title[]{Modelling fine-scale dive behavior with hidden Markov models }%\query{Q1}
\author{BlindedA\authorref{1}\thanksref{*}}
\author{BlindedB\authorref{2}}
\affiliation[1]{Author affiliations will go here in the accepted manuscript, 
but do NOT include them in your initial submission because it must be anonymous.}
\affiliation[2]{Second Affiliation}

@@

Recent advances in high-frequency tagging
technology have made available a vast
amount of animal movement data. This
rich new data can exhibit simultaneous behavioural processes occurring at different
time scales. One can model these processes
through a hierarchical hidden Markov model
(HHMM), where the system is modelled as a
nested structure of hidden Markov models.
At very short time scales, however, observations can exhibit complicated dependence
structures that cannot be easily captured by
traditional HMMs. We demonstrate how
to incorporate fine-scale processes into the
larger structure of HHMMs while maintaining computational efficiency. We apply our
method to dive and accelerometer data collected from northern resident killer whales off
the coast of British Columbia, Canada.

@@

% Email address for corresponding author
\correspondingauthor[*]{\\\email{Insert your email address here only after your paper has been accepted}}

%\input Sections/intro.tex
\input Sections/background.tex
\input Sections/carhmm_ou.tex
\input Sections/model.tex
\input Sections/simulation.tex
%\input Sections/results.tex
%\input Sections/conclusion.tex

\clearpage

\bibliographystyle{plain}
\bibliography{references}

\clearpage

\input Sections/appendix.tex

>>>>

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{psfrag}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{url}
\input{header}
\input{defs}

@@

% User-defined commands go here
\renewcommand{\eqref}[1]{(\ref{#1})}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mt}[1]{\mathrm{#1}}
\newcommand{\rv}{random variable}
\newcommand{\newblock}{}
\bibliographystyle{abbrvnat}

% Title, authors, affiliations
\title[]{Modelling fine-scale correlation structures using hidden Markov models}%\query{Q1}
\author{BlindedA\authorref{1}\thanksref{*}}
\author{BlindedB\authorref{2}}
\affiliation[1]{Author affiliations will go here in the accepted manuscript, 
but do NOT include them in your initial submission because it must be anonymous.}
\affiliation[2]{Second Affiliation}

@@

Recent advances in high-frequency tagging
technology have made available a vast
amount of movement data in a variety of fields. This
rich new data can exhibit simultaneous behavioural processes occurring at different
time scales, resulting in very complicated dependence structures. One can model these processes
through a hierarchical hidden Markov model
(HHMM), where the system is modelled as a
nested structure of hidden Markov models.
At very short time scales, however, many assumptions of traditional HMMs are violated. We demonstrate how
to incorporate fine-scale processes into the
larger structure of HHMMs while maintaining computational efficiency. We apply our
method to dive and accelerometer data collected from a northern resident killer whale off
the coast of British Columbia, Canada.

@@

% Email address for corresponding author
%\correspondingauthor[*]{\\\email{}} % only put this in after acceptance

%%%%%%%%%%%%
\vfill\eject
{\centerline{\Large{Notes from Nancy}}}
\input{Sections/0627NH}
\vfill\eject
%%%%%%%%%%%%%
%
\section{Introduction}
\input Sections/intro.tex
%
\section{Models and parameter estimation}
\input Sections/models.tex
%
\section{Simulation Study}
\input Sections/simulation.tex
%
\section{Killer Whale Case Study}
\label{sec:case_study}
\input Sections/results.tex
%
\section{Discussion}
\input Sections/discussion.tex
%
\newpage
\bibliography{references}
%
\newpage
\begin{appendix}
\input Sections/appendix.tex
\end{appendix}
%
\newpage
\section{Figures and Tables}
\input Sections/figures.tex
%
%\CJShistory
